%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Updates/fixes author: John Guidry
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	Packages and Other Configurations
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.3in]{geometry}
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{John Guidry} % Name
\address{3310 Chrysanthemum Way, Raleigh, NC 27614} % Address
\address{\url{https://github.com/JohnGuidry}}
\address{(540)267-4470 \\ john.guidry92@gmail.com} % Phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	Professional Summary - Removed due to conflicting opinions
%----------------------------------------------------------------------------------------

%\begin{rSection}{Professional Summary} 
%Dynamic Software Engineer skilled in developing complex solutions and possessing strong creative thinking skills, high energy and integrity.
%\end{rSection}

%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\begin{multicols}{3}
\begin{enumerate}
\begin{itemize}
\item XML and XSLT
\item Microsoft SQL Server
\item Software Documentation
\item C\# 
\item IIS
\item New Employee Mentoring
\item Code Reviews
\item Build Releases
\item Agile
\item LaTeX
\item JIRA
\end{itemize}
\end{enumerate}
\end{multicols}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Work History
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

{\bf Software Engineer II, }{\em June 2015 - Present} 
\\
{\bf Public Consulting Group -  }{\em Blacksburg, VA}
\begin{itemize}
\item Wrote SQL scripts for daily maintenance activities, including tables analyses involving multiple JOINS, UNIONS, and CTE's.
\item Modified preexisting scalable applications for information identification, extraction, analysis, and retrieval using C\# and SQL.
\item Versed in complete software life cycle from preliminary needs analysis to enterprise-wide deployment and support.
\item Modified existing software to correct coding errors, upgrade interfaces and improve overall performance.
\item Directed software design and development while remaining focused on meeting client needs for functionality, timeline, and performance.
\item Consulted regularly with internal customers on application development project status, new project proposals, and software-related technical issues.
\item Worked effectively with cross-functional design teams to create software solutions that elevated client side experience and significantly improved overall functionality and performance.
\item Orchestrated efficient deployments, including testing features and correcting code to produce innovative products.
\item Gathered and defined customer requirements to develop well-organized project plans based on clear specifications.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%    Education
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Bachelor of Science: }{\em Computer Science with a minor in Mathematics, 2015} 
\\
{\bf Roanoke College -  }{\em Salem, VA}
\begin{itemize}
\item Elected to President for Roanoke College Student Chapter of Association for Computing Machinery in 2014.
\item Elected to Vice President for Roanoke College Student Chapter of Association for Computing Machinery in 2013.
\end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Industry Hobbies
%----------------------------------------------------------------------------------------

\begin{rSection}{Industry Hobbies} 
{\bf Cyrptocurrency Mining Management, }{\em June 2017 - August 2018} 
\\
{\bf Git: }\url {https://github.com/JohnGuidry/puddle_jumper}
\begin{itemize}
\item Maintained a cryptocurrency mining machine using Linux and perl scripts to identify profitable 'alt coins.'
\item Created power failure scripts for boot.
\item Created boot scripts to call overclocking of graphics cards and perl scripts to mine.
\end{itemize}

{\bf This resume was written in LaTeX: }\url{https://github.com/JohnGuidry/documentation}
\end{rSection}
\end{document}
